---
title: "6306_hw4_SGu"
author: "Shanqing Gu"
date: "1/31/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## HW4_Question 1: FiveThirtyEight Data

# 1a. Install the fivethirtyeight package
```{r fivethirtyeight}
library(fivethirtyeight)
```

# 1b. In the list of Data sets in package 'fivethirtyeight', assign the 18th data set to an object 'df'

```{r df}
dp <- data(package="fivethirtyeight")
df <- college_recent_grads
```

# 1c. Use a more detailed list of the data sets to write out the URL in a comment to the relaed news story
```{r fivethirtyeight package}
vignette("fivethirtyeight", package = "fivethirtyeight")
```

* Story about: http://fivethirtyeight.com

# 1d. Give the diamensions and column names of this data frame
```{r dim}
dim(df)
colnames(df)
```

## HW4_Question 2: Data summary

# 2a. ncol
```{r col1}
ncol(df)
```

# 2b. Generate a count of each unique major_catergory in the data frame.

```{r col2}
library("plyr")
require(plyr)

major_count <- as.data.frame(table(df$major_category))
major_count

```

#2c Barplot of major_count

```{R barplot}
par(mai=c(1,4,1,1))
barplot (major_count$Freq, las=2, horiz=TRUE, main = " The Economic Guide To Picking A College Major", xlab = "Major Category Frequency", col=rgb(0.2,0.4,0.6,0.6), names.arg=(major_count$Var1), font=1)
title(ylab="Major", mgp=c(16,1,0), cex.lab=1.2)
```

#2d Write the fivethirtyeight data to a csv file

```{R csv}
write.csv(df, file = "df538.csv", row.names=FALSE)
```

## HW_Questions 3: Codebook

## https://github.com/guvp2017/SMU6306.git