---
title: "6306_hw3_SGu"
author: "Shanqing Gu"
date: "1/27/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## HW3_Q1: GitHub Cloning

* Using Git, clone one repositiory to my mac:
git clone https://github.com/awesomedata/awesome-public-datasets.git

* Creat a new directory with code:  mkdir hw3/q1

* navigate to a new directory:   cd awesome-public-datasets

* clone the repositiory to hw3:  cp -r awesome-public-datasets myrepo/hw3


## HW3_Q2: Data Summary

* a. Read in titanic.csv via read.csv and assign it to df. This dataset follows the passengers aboard the Titanic, including their fees paid, rooms rented, and survivorship status.

```{r df} 
df= read.csv("/Users/shanqinggu/Desktop/titanic.csv", header = TRUE)
```

* b. Plot the frequency of females and males aboard the Titanic.

```{r Frequency} 
df= read.csv("/Users/shanqinggu/Desktop/titanic.csv", header = TRUE)
df$Sex <- as.factor(df$Sex)
plot(df$Sex, main="Respective count of females and males aboard Titanic", xlab= "Sex Distribution", ylab= "Frenquency")
```

* c. Output the means of Age, Fare, and Survival.

```{r means} 
df= read.csv("/Users/shanqinggu/Desktop/titanic.csv", header = TRUE)
mAge=apply(as.matrix(df$Age),2,mean,na.rm=TRUE)
mAge
mFare=apply(as.matrix(df$Fare),2,mean,na.rm=TRUE)
mFare
mSurvived= apply(as.matrix(df$Survived),2,mean,na.rm=TRUE)
mSurvived
```

## HW3_Q3: Function building

```{r Function}

## a. Creat objects for MedianAge, Rdurations, MeanRSES5, SdRSES5.
sleep <- read.csv("/Users/shanqinggu/Desktop/sleep_data_01.csv", header = TRUE)

# MedianAge
MedianAge <- apply(as.matrix(sleep$Age),2,median,na.rm=TRUE)

# Rduration
Rduration1 <- apply(as.matrix(sleep$Duration), 2, range, na.rm=TRUE)[2,] 
Rduration2 <- apply(as.matrix(sleep$Duration), 2, range, na.rm=TRUE)[1,]
Rduration <- Rduration1-Rduration2

# MesnRSES
MeanRSES <- apply(as.matrix(sleep$RSES), 2, mean, na.rm=TRUE)

# SdRSES
SdRSES <- apply(as.matrix(sleep$RSES), 2, sd, na.rm=TRUE)


## b. Create a data.frame object called report
catVars <- c("MedianAge","MeanRSES","SdRSES", "Rduration")
Values <- c(MedianAge, MeanRSES, SdRSES, Rduration)
report <-data.frame("MedianAge"=MedianAge, "MeanRSES"=MeanRSES, "SdRSES"=SdRSES, "Rduration"=Rduration)
report


## c. Change column names to MedianAge, SelfEsteem, SE_SD and DurationRange
report=setNames(report, c("MedianAge", "SelfEsteem", "SE_SD", "DurationRange"))
report

## d. Round the report to at most 2 digits: leaving this as as the closing line to the function
report <- round(report, digits=2)

## e. Run the function on sleep data to show the output
report
```