---
title: "SGu_6306_HW5"
author: "Shanqing Gu"
date: "2/10/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## MSDS-6306 Unit 05 Homework Assignment

# Q1: Data Munging

# Q1_a: Import yob2016.txt file into R and assign df which consists 3 columns with names.

```{r q1a}
df <- read.table("/Users/shanqinggu/Desktop/yob2016.txt", header=FALSE, sep=";")
df <- as.data.frame(df)
colnames(df) <- c("Names", "Sex", "Year_2016")
head(df)
```

# Q1_b: Display the summary and structure of df

```{r q1b}
summary(df)
str(df)
```

# Q1_c: Find name with three y's at the end of them
```{r q1c}
grep("yyy", df$Names, value=TRUE)
```

# Q1_d: Remove redundant observation and save the remaining dataset as y2016
```{r q1d}
y2016 <- subset(df, Names!="Fionayyy")
```

# Q2: Data Merging

# Q2_a: Import yob2015.txt file into R and assign df2 which consists 3 columns with names.

```{r q2a}
df2 <- read.table("/Users/shanqinggu/Desktop/yob2015.txt", header=FALSE, sep=",")
df2 <- as.data.frame(df2)
colnames(df2) <- c("Names", "Sex", "Year_2015")
head(df2)
```

# Q2_b: Display last ten rows and describe

```{r q2b}
tail(df2,10)
```
# Interesting to me is all the names are boy names.

# Q2_c: Merge y2016 and y2015 by Name column and assign it to final
```{r q2c}
final <- merge.data.frame(df, df2, by="Names", all=FALSE)
head(final)
```

# Q3: Data Summary

# Q3_a: Creat a new column called "Total" in final and add together to address how many people were given popular names.
```{r q3a}
Total <- final$Year_2015 + final$Year_2016
final.total <- cbind(final, Total)
sum(final.total$Total)
```

# Q3_b: Sort the data by Total and list the top 10 most popular names
```{r q3b}
final.sort <- final.total[order(final.total$Total,decreasing=TRUE),]
head(final.sort, 10)
```

# Q3_c Top 10 most poular girl's names
```{r q3c}
final.girls<-final.sort[final.sort$Sex.x=="F" & final.sort$Sex.y=="F",]
girls.top10 <- head(final.girls,10)
girls.top10
```

# Q3_d Write these top 10 girl names and their Totals to a csv file
```{r q3d}
write.csv(girls.top10[,c("Names","Total")], file="girlsTop10.csv",row.names=FALSE)
```

# Q4: Upload to GitHub

# https://github.com/guvp2017/SMU6306.git