---
title: "SGu_6306_HW_09"
author: "Shanqing Gu"
date: "3/10/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Libraries used for this assignment: MSDS 6306_Unit-09
library(xml2)
library(rvest)
library(tidyr)
library(ggplot2)
```

## Q1: Harry Porter Cast

#### Q1a: Navigate webpage: "http://www.imdb.com/title/tt1201607/fullcredits?ref_=tt_ql_1" 

#### Q1b: Scrape the cast list table and make it a data frame

```{r Q1b}

# Read webpage
webpage <- 'http://www.imdb.com/title/tt1201607/fullcredits?ref_=tt_ql_1' 
HarryPorter <- xml2::read_html(webpage) 

# Scrape the table of interest and make it a data frame

CastList <- rvest::html_nodes(HarryPorter, xpath = '//*[@id="fullcredits_content"]/table[3]')
CastTable <-rvest::html_table(CastList)
CastData <- data.frame(CastTable)
```

#### Q1c: Clean up the table with requirements (no blank observations, add column names, fix Mr. Warwick issue, remove specific row #93)

```{r Q1c}
# Remove 1st blank row and 2 blank columns 
CastData <- CastData[-1, -c(1,3)]

# Add column names
colnames(CastData) <- c("Actor/Actress", "Character")

# Rmeove one row contains "Rest of cast listed alphabetically"
CastRemove <- subset(CastData, Character!="Rest of cast listed alphabetically:")

# Find name contains "Warwick"
grep("Warwick", CastData$'Actor/Actress', value=TRUE)

# Replace with "Griphook / Professor Filius Flitwick"
CastRemove[10,2]=gsub('\n','',CastRemove[10,2])

# Rewrite the row numbers
rownames(CastRemove) <- 1:nrow(CastRemove)
```

#### Q1d: Split the actor/actress name into two columns
```{r Q1d}
# Split names to firstnames and lastnames
SplitNames <- tidyr::extract(CastRemove, "Actor/Actress", c("FirstName", "LastName"), "(.*) ([^ ]+)$")
```

#### Q1e: Present the first 10 rows of this data frame
```{r Q1e}
Top10List<-head(SplitNames, 10)
Top10List
```
## Q2: Sports Ball

#### Q2a: Navigate webpage: "http://www.espn.com/nba/team/stats/_/name/sa/san-antonio-spurs""

#### Q2b: Scrape the "Shooting Statistics" table

```{r Q2b}
webpage <- 'http://www.espn.com/nba/team/stats/_/name/sa/san-antonio-spurs'
Shooting <- read_html(webpage)
ShStat <- rvest::html_nodes(Shooting, xpath='//*[@id="my-players-table"]/div[3]/div[3]/table')
StatTable <- rvest::html_table(ShStat)
TableFrame <- data.frame(StatTable)
```

#### Q2c: Clean the table

```{r Q2c}
# Remove the first 2 rows with row names and the last total row
TableRemove <- TableFrame [-c(1,2,20),]
rownames(TableRemove) <- 1:nrow(TableRemove) # Update row index

# Split names and postions
names(TableRemove)[1] <- paste("Player")
TableSplit <- separate(TableRemove, col=Player, into=c('Name', 'Position'), sep=", ")
head(TableSplit)

#Convert relevant columns to numeric vectors
sapply(TableSplit,mode)
TableSplit[,3:ncol(TableSplit)] <- sapply(TableSplit[,3:ncol(TableSplit)],as.numeric)
sapply(TableSplit, class)
```

#### Q2d: Creat a colorful bar chart

```{r Q2d}
# Order by decreasing field goals percentage  
TableOrder <- TableSplit[order(TableSplit$X4, decreasing=FALSE),]

# Make bar chart with ggplot2 
ggplot(TableOrder, aes(reorder(Name, `X4`),`X4`, fill=Position)) + geom_bar(stat="identity") +
ggtitle('Field Goals Percentage Per Game') +
ylab('Field Goals Percentage Per Game')	+ xlab('Player Name') +
theme(plot.title=element_text(hjust = .5), axis.ticks.y=element_blank(),axis.ticks.x=element_blank()) +
theme(axis.text.x = element_text(angle=60,hjust=1))
```




#### GitHub address for this assignment (MSDS 6306_Unit 09): 

https://github.com/guvp2017/SMU6306.git